A Global Market for Marine Conservation

### 2021-11-09 draft.Rmd

The motivation from a market-based approach to conservation relies on two premises. First, that habitat worth protecting is heterogeneously distributed across nations. And, secondly, that the costs of protecting habitat are non-perfectly correlated with the protection value of the pixel. Together, these two features make it possible to lower costs by using trade to protect the most cost-effective places. The magnitude of market gains (that is, cost savings relative to BAU unilateral conservation with no trade) will depend on the correlation between costs and benefits. To illustrate this point, we generate synthetic data to simulate 20 girded worlds where the conservation value of a pixel is heterogeneously distributed, and where costs and benefits exhibit varying degrees of correlation (R from -1 to 1; See methods for a detailed description on synthetic data generation). For each scenario, we calculate the gains from trade for a series of protection targets (1 - 100%). We find that unless the costs and benefits are perfectly correlated (\emph{i.e.} R = 1), a market will always lower the costs of conservation for any desired target.

@@

![\label{fig:rlm-map-of-trade}Map of trade for each realm. Blue indicates nations that reach the trading price before meeting their target, and therefore chose to pay to conerve elsewhere. Red nations get paid to conserve in their waters, due to the low costs relative to blue nations.](results/img/rlm_map_of_trade.png)

@@

![\label{fig:realms-per-eezs} Number of realms in each Exclusive Economic Zone](results/img/realms_per_eez.png)

>>>>

The motivation from a market-based approach to conservation relies on two premises. First, that habitat worth protecting is heterogeneously distributed across nations. And, secondly, that the costs of protecting habitat are non-perfectly correlated with the protection value of the pixel and are thus also heterogeneous in space. Together, these two features make it possible to lower costs of conservation by using trade to protect the most cost-effective places. The magnitude of market gains (that is, cost savings relative to BAU unilateral conservation with no trade) will depend on the spatial distribution of costs and benefits. To illustrate this point, we generate synthetic data to simulate girded worlds where the conservation value of a pixel is heterogeneously distributed, and where costs and benefits exhibit different correlation coefficients (R from -1 to 1; See methods for a detailed description on synthetic data generation). For each scenario, we calculate the gains from trade for a series of protection targets (1 - 100%). We find that unless the costs and benefits are spatially homogeous and perfectly correlated (\emph{i.e.} R = 1), a market will always lower the costs of conservation for any desired target.

@@

![\label{fig:rlm-map-of-trade}Map of trade for each Hemisphere. Blue indicates nations that reach the trading price before meeting their target, and therefore chose to pay to conerve elsewhere. Red nations get paid to conserve in their waters, due to the low costs relative to blue nations.](results/img/map_of_trade_hem.png)

@@
